Learning by Teaching a Robot:\\The Case of Handwriting

### 2015-12-15 main.tex
WIP on the conclusion

>>>>

As we show through extensive experimental validation, these claims are not just
words: we have effectively deployed robots on the field, with children suffering
actual handwriting impairments. Our results are promising in terms of sustaining
the interest and attention of children on otherwise boring writing exercises,
and we evidence clear handwriting improvements.

It is however still early to quantify the lasting effects of this remediation:
handwriting is a complex cognitive skill, that builds on many individual and
social factors. Self-confidence is one of them. We expect that our
approach that endows the child with the role of a teacher who can help a robot,
may help some children to recover self-esteem and self-confidence. However the
experiments that we have conducted so do not allow us to confirm this
hypothesis, and more research need to be conducted in this direction.
